Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-19 paper.tex
bib shortened
shrink: merge regret reward in one formula

The simulations are publicly available at \url{https://github.com/AggregateComputing/experiment-2023-acsos-field-informed-rl}.

@@

The final reward function for an agent $v$ is defined as:

@@

R_{v} = \frac{R^a_{v} + R^{\mathcal{N}}_{v} + R^{C}_{v}}{3}

@@

It is simplify evaluated as:
R^e_{v} = R_v - 1

>>>>

\footnote{The simulations are publicly available at \url{https://github.com/AggregateComputing/experiment-2023-acsos-field-informed-rl}.}

@@

The final reward function $R_{v}$ for an agent $v$ is defined as:

@@

R_{v} = (\frac{R^a_{v} + R^{\mathcal{N}}_{v} + R^{C}_{v}}{3}) - 1

@@
